---
title: "Untitled"
author: "Ozum"
date: "1/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dependencies, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(readr)
```

- How does various factors (economic production, social support, life expectancy, freedom, absence of corruption, and generosity) affect happiness in a country?

- How do countries compare in terms of happiness vs. some other factor?

- How do regions compare in terms of happiness vs. some other factor?

- How has happiness and happiness indicators improved over time for a specific country?


```{r import_data, message=FALSE}
happiness2017 <- read_csv("data/happiness_2017.csv")
happiness2016 <- read_csv("data/happiness_2016.csv")
happiness2015 <- read_csv("data/happiness_2015.csv")
```

```{r}
names(happiness2015) <- c("Country", "Region", "Happiness.Rank", "Happiness.Score", "Standard.Error", "Economy", "Family", "Health", "Freedom", "Government.Corruption", "Generosity", "Dystopia.Residual")

happiness2015 %>% arrange(Happiness.Rank) %>% select(Happiness.Rank, Country) %>% top_n(10, desc(Happiness.Rank))

df <- data.frame(x = c(10, 4, 1, 6, 3, 1, 1))
df %>% top_n(2)

h15 <- happiness2015 %>% select(Country)
h16 <- happiness2016 %>% select(Country)
h17 <- happiness2017 %>% select(Country)

unique(rbind(h15, h16, h17))


range(happiness2015$Happiness.Score)
```

